StarCraft Bots and Competitions

### 2015-12-17 ECGG_StarCraftCompetitions/ECGG_StarCraftCompetitions.tex
some final little fixes

\begin{table}[!t]
\caption{Ranking of the best bots of the SSCAIT 2012 competition (52 participants)}
\label{tab:sscait2012}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{Student division} & \multicolumn{2}{|c|}{Mixed division}\\
{\bfseries Rank} & {\bfseries Bot} & {\bfseries Rank} & {\bfseries Bot} \\
\hline
1 & Matej Isten\'{i}k's bot & 1 & ICEBot \\
2 & Marcin Bartnicki's bot  & 2 & Marcin Bartnicki's bot \\
3 & UAlbertaBot 			&   &  \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[!t]
\caption{Ranking of the best bots of the SSCAIT 2013 competition (50 participants).
The student division winner was determined by means of 1190 round-robin games}
\label{tab:sscait2013}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{Student division} & \multicolumn{2}{|c|}{Mixed division}\\
{\bfseries Rank} & {\bfseries Bot} & {\bfseries Rank} & {\bfseries Bot} \\
\hline
1 & Ximp & 1 & Krasi0 \\
2 & W.O.P.R.  & 2 & ICEBot \\
3 & UAlbertaBot 			&   &  \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[!t]
\caption{Ranking of the best bots of the SSCAIT 2014 competition (42 participants).
The student division winner was determined by means of 861 round-robin games}
\label{tab:sscait2014}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{Student division} & \multicolumn{2}{|c|}{Mixed division}\\
{\bfseries Rank} & {\bfseries Bot} & {\bfseries Rank} & {\bfseries Bot} \\
\hline
1 & LetaBot & 1 & LetaBot \\
2 & W.O.P.R.  & 2 & Ximp \\
3 & UAlbertaBot 			&   &  \\
\hline
\end{tabular}
\end{table}

>>>>

\begin{table}[!t]
\caption{Ranking of the best bots of the SSCAIT 2012 competition (52 participants)}
\label{tab:sscait2012}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{Student division} & \multicolumn{2}{|c|}{Mixed division}\\ \hline
{\bfseries Rank} & {\bfseries Bot} & {\bfseries Rank} & {\bfseries Bot} \\
\hline
1 & Matej Isten\'{i}k's bot & 1 & ICEBot \\
2 & Marcin Bartnicki's bot  & 2 & Marcin Bartnicki's bot \\
3 & UAlbertaBot 			&   &  \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[!t]
\caption{Ranking of the best bots of the SSCAIT 2013 competition (50 participants).
The student division winner was determined by means of 1190 round-robin games}
\label{tab:sscait2013}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{Student division} & \multicolumn{2}{|c|}{Mixed division}\\ \hline
{\bfseries Rank} & {\bfseries Bot} & {\bfseries Rank} & {\bfseries Bot} \\
\hline
1 & Ximp & 1 & Krasi0 \\
2 & W.O.P.R.  & 2 & ICEBot \\
3 & UAlbertaBot 			&   &  \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[!t]
\caption{Ranking of the best bots of the SSCAIT 2014 competition (42 participants).
The student division winner was determined by means of 861 round-robin games}
\label{tab:sscait2014}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{Student division} & \multicolumn{2}{|c|}{Mixed division}\\ \hline
{\bfseries Rank} & {\bfseries Bot} & {\bfseries Rank} & {\bfseries Bot} \\
\hline
1 & LetaBot & 1 & LetaBot \\
2 & W.O.P.R.  & 2 & Ximp \\
3 & UAlbertaBot 			&   &  \\
\hline
\end{tabular}
\end{table}
